Timid tides or tall tails? \\ Investigating the outer reaches of the Sculptor and Ursa Minor dwarf galaxies

### 2025-04-08 thesis/data.tex
fixes compiling and warnings

Fornax(figures/fornax\_selection.png)\{\#fig:fornax\_selection\}

@@

In Figures fig.~\ref{fig:scl_observed_profiles},
fig.~\ref{fig:umi_observed_profiles},
\citet{fig_fornax_observed_profiles}, we show the derived density
profiles for each galaxy for samples similar to in the selection plots
above. In each case, all samples are the same towards the inner regions
of the satellite, illustrating that these density profiles are dominated
by satellite stars in the centre. The sample containing all stars
reaches a plateau at the total background in the field. However,
restricting stars to being most likely satellite members by CMD + PM,
the background is much lower. This plateau likely represents the real
background of background stars which could be mistaken as members.
Finally, we have the probable members and bg-subtracted densities. BG
subtracted is based on the \texttt{all} density profile, subtracting the
mean background density for stars beyond the last point of the BG
subtracted profile.

>>>>

@@

In Figures fig.~\ref{fig:scl_observed_profiles},
fig.~\ref{fig:umi_observed_profiles}, we show the derived density
profiles for each galaxy for samples similar to in the selection plots
above. In each case, all samples are the same towards the inner regions
of the satellite, illustrating that these density profiles are dominated
by satellite stars in the centre. The sample containing all stars
reaches a plateau at the total background in the field. However,
restricting stars to being most likely satellite members by CMD + PM,
the background is much lower. This plateau likely represents the real
background of background stars which could be mistaken as members.
Finally, we have the probable members and bg-subtracted densities. BG
subtracted is based on the \texttt{all} density profile, subtracting the
mean background density for stars beyond the last point of the BG
subtracted profile.
